---
title: "DualTasking"
author: "Kejing Yan"
date: "2023-10-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(writexl)
library(car)
library(ggplot2)
library(dplyr)
library(mclust)
library(randomForest)
library(gbm)
library(xgboost)
```

1. Initial baseline walk
2. walk w/ low obstacle
3. walk w/ medium obstacle
4. walk w/ high obstacle
5. typing while walk
6. texting while walk
7. typing while walk w/ low obstacle
8. texting while walk w/ low obstacle  
9. typing while walk w/ medium obstacle
10. texting while walk w/ medium obstacle  
11. typing while walk w/ high obstacle
12. texting while walk w/ high obstacle  
13. final baseline walk

```{r, include = FALSE}
data <- data.frame(matrix(nrow = 468, ncol = 20))
colnames(data) <- c('ID', 'Condition',	'Trial',	'Mean Step Length (cm.)',	'Mean Stride Length (cm.)',	'Stride Width (cm.)',	'Step Time (sec.)',	'Stride Time (sec.)',	'Total D. Support (sec.)',	'Velocity (cm./sec.)',	'Cadence (steps/min.)',	'%CV Step Length (cm.)',	'%CV Stride Length (cm.)',	'%CV Stride Width (cm.)',	'%CV Step Time (sec.)',	'%CV Stride Time (sec.)',	'%CV Total D. Support (sec.)', 'Gender', 'Obstacle', 'Task')
```

## Create excel file
```{r, eval = FALSE, include = FALSE}
count = 1

  for (j in 1:13) {
      for (k in 1:3) {
        
        zeros <- '00'
        
        filename = paste(zeros, 1, sep = '')
        subname = paste('cond', j, '0', k, sep = '')
        filename = paste('TWWT/', filename, '/', subname, '.xlsx', sep = '')
        
        fullname1 = paste("C:/Users/闫可菁/Dropbox/Research/Motor Development Lab/", filename, sep = '')
        fullname2 = paste("C:/Users/闫可菁/Dropbox/Research/Motor Development Lab/", 'TWWT/', zeros, 1, '/', subname, '_info.xlsx', sep = '')
        
        if (file.exists(filename)) {
          if (file.info(fullname1)$size < file.info(fullname2)$size) {
            filename <- paste("TWWT/", zeros, 1, "/", subname, "_info.xlsx", sep = '')
          }
        }
        
        #print(filename)
          
        if (file.exists(filename)) {
          inputdata <- read_excel(filename, range = "C12:AZ23", col_types = c("numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric"))
            
            data[count, 1] = 1
            data[count, 2] = j
            data[count, 3] = k
            data[count, 4:11] = inputdata[4,c(16, 18:21, 35, 48, 50)]
            data[count, 12:17] = inputdata[11, c(16, 18:21, 35)]
            
            inputdata2 <- read_excel(filename, range = 'B3', col_names = FALSE)
            data[count,18] <- inputdata2
          
            
        } else {
            data[count, 1] = 1
            data[count, 2] = j
            data[count, 3] = k
            data[count, 4:17] = NA
            data[count, 18] = NA
        }
        
        if (j %in% c(1,5,6,13)) data[count,19] <- 0
        if (j %in% c(2,7,8)) data[count, 19] <- 1
        if (j %in% c(3,9,10)) data[count, 19] <- 2
        if (j %in% c(4,11,12)) data[count, 19] <- 3
        
        if (j %in% c(1,2,3,4,13)) data[count,20] <- 0
        if (j %in% c(5,7,9,11)) data[count, 20] <- 1
        if (j %in% c(6,8,10,12)) data[count, 20] <- 2
        
        count = count + 1
      }
  }



for (i in 2:12) {
  for (j in 1:13) {
      for (k in 1:3) {
        
        if (i < 10) {
          zeros <- '00'
        } else {
          zeros <- '0'
        }
        
        filename = paste(zeros, i, sep = '')
        subname = paste(j, '0', k, sep = '')
        filename = paste('TWWT/', filename, '/', subname, '.xlsx', sep = '')
        
        fullname1 = paste("C:/Users/闫可菁/Dropbox/Research/Motor Development Lab/", filename, sep = '')
        fullname2 = paste("C:/Users/闫可菁/Dropbox/Research/Motor Development Lab/", 'TWWT/', zeros, i, '/', subname, '_info.xlsx', sep = '')
        
        if (file.exists(filename)) {
          if (file.exists(fullname2)) {
            if (file.info(fullname1)$size < file.info(fullname2)$size) {
              filename <- paste("TWWT/", zeros, i, "/", subname, "_info.xlsx", sep = '')
            }
          }
        }
        
        #print(filename)
          
        if (file.exists(filename)) {
          inputdata <- read_excel(filename, range = "C12:AZ23", col_types = c("numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric"))
            
            data[count, 1] = i
            data[count, 2] = j
            data[count, 3] = k
            data[count, 4:11] = inputdata[4,c(16, 18:21, 35, 48, 50)]
            data[count, 12:17] = inputdata[11, c(16, 18:21, 35)]
            inputdata2 <- read_excel(filename, range = 'B3', col_names = FALSE)
            data[count,18] <- inputdata2
            
          
        } else {
            data[count, 1] = i
            data[count, 2] = j
            data[count, 3] = k
            data[count, 4:17] = NA
            data[count, 18] = NA
        }
        
        if (j %in% c(1,5,6,13)) data[count,19] <- 0
        if (j %in% c(2,7,8)) data[count, 19] <- 1
        if (j %in% c(3,9,10)) data[count, 19] <- 2
        if (j %in% c(4,11,12)) data[count, 19] <- 3
        
        if (j %in% c(1,2,3,4,13)) data[count,20] <- 0
        if (j %in% c(5,7,9,11)) data[count, 20] <- 1
        if (j %in% c(6,8,10,12)) data[count, 20] <- 2
        
        count = count + 1
      }
  }
}
```


```{r, eval = FALSE, include = FALSE}
write_xlsx(data,"TWWT_fulldata.xlsx")
```


```{r}
data <- read_excel("TWWT_fulldata.xlsx")
```


## Create dataframe of averaged data
```{r}
data_avg <- data.frame(matrix(nrow = 156, ncol = 23))

for (i in seq(1, 468, by = 3)) {
  j = (i+2)/3
  data_avg[j,1:2] = data[i,1:2]
  for (k in c(4:17, 21:23)) {
    num1 = as.numeric(data[i, k])
    num2 = as.numeric(data[i+1, k])
    num3 = as.numeric(data[i+2, k])
    if (is.na(num1) && is.na(num2) && is.na(num3)) {
      data_avg[j,k] = NA
    } else {
      count = 3
      if (is.na(num1)){
        num1 = 0
        count = count - 1
      }
      num2 = as.numeric(data[i+1, k])
      if (is.na(num2)){
        num2 = 0
        count = count - 1
      }
      num3 = as.numeric(data[i+2, k])
      if (is.na(num3)){
        num3 = 0
        count = count - 1
      }
      data_avg[j, k] = (num1+ num2+ num3)/count
    }
  }
  for (k in 18:20) {
    if (is.na(data[i,k]) != TRUE) {
        data_avg[j, k] <- data[i, k]
    } else if (is.na(data[i+1,k]) != TRUE){
      data_avg[j, k] <- data[i+1, k]
    } else {
      data_avg[j, k] <- data[i+2, k]
    }

  }
}

data_avg = data_avg[,-3]
colnames(data_avg) = colnames(data)[-3]

```


## Kmeans Clustering
```{r}
#copy data into a new dataframe with 17 independent variables
cluster.data <- data_avg[,-c(1,2,18,19,22)]
cluster.data$Gender <- ifelse(data_avg$Gender == "female", 1, 0)
cluster.data[,1:14] <- scale(cluster.data[,c(1:14,16:17)])
cluster.data <- na.omit(cluster.data)

#cluster with 4 centers (conjecturing that four groups will correspond to four different obstacle height)
cl <- kmeans(cluster.data, centers = 4)

#copy cluster result into dataframe
plot_data <- na.omit(data_avg[,-c(22)])
plot_data$Cluster <- as.factor(cl$cluster)

plot_data$Obstacle <- as.factor(plot_data$Obstacle)
plot_data$Task <- as.factor(plot_data$Task)

```
### Cluster with 4 centers
```{r}
# Perform PCA
pca_result <- prcomp(cluster.data, rank. = 2)  # reduce to 2 dimensions for visualization

loadings <- pca_result$rotation

# Add PCA results to the original data frame
plot_data$PC1 <- pca_result$x[, 1]
plot_data$PC2 <- pca_result$x[, 2]

# Use ggplot2 to create the PCA scatter plot colored by clusters
ggplot(plot_data, aes(x = PC1, y = PC2, color = as.factor(Cluster))) +
  geom_point() +
  scale_color_manual(values = c("purple", 'steelblue', 'green', 'orange','pink','grey','black','darkblue','darkgreen','yellow','blue','red')) + # Customize colors if needed
  theme_minimal() +
  labs(title = "PCA of k-Means Clusters (4 Centers)", color = "Cluster")

```

```{r}
#copy data into a new dataframe with 17 independent variables
cluster.data <- data_avg[,-c(1,2,18,19,22)]
cluster.data$Gender <- ifelse(data_avg$Gender == "female", 1, 0)
cluster.data[,1:14] <- scale(cluster.data[,c(1:14,16:17)])
cluster.data <- na.omit(cluster.data)

#cluster with 3 centers (conjecturing that four groups will correspond to three different task)
cl <- kmeans(cluster.data, centers = 3)

#copy cluster result into dataframe
plot_data <- na.omit(data_avg[,-c(22)])
plot_data$Cluster <- as.factor(cl$cluster)

plot_data$Obstacle <- as.factor(plot_data$Obstacle)
plot_data$Task <- as.factor(plot_data$Task)

```

### Cluster with 3 centers
```{r}
# Perform PCA
pca_result <- prcomp(cluster.data, rank. = 2)  # reduce to 2 dimensions for visualization

loadings <- pca_result$rotation

# Add PCA results to the original data frame
plot_data$PC1 <- pca_result$x[, 1]
plot_data$PC2 <- pca_result$x[, 2]

# Use ggplot2 to create the PCA scatter plot colored by clusters
ggplot(plot_data, aes(x = PC1, y = PC2, color = as.factor(Cluster))) +
  geom_point() +
  scale_color_manual(values = c("purple", 'steelblue', 'green', 'orange','pink','grey','black','darkblue','darkgreen','yellow','blue','red')) + # Customize colors if needed
  theme_minimal() +
  labs(title = "PCA of k-Means Clusters (3 Centers)", color = "Cluster")

```


### Cluster with 12 centers
```{r}
#copy data into a new dataframe with 17 independent variables
cluster.data <- data_avg[,-c(1,2,18,19,22)]
cluster.data$Gender <- ifelse(data_avg$Gender == "female", 1, 0)
cluster.data[,1:14] <- scale(cluster.data[,c(1:14,16:17)])
cluster.data <- na.omit(cluster.data)

#cluster with 12 centers (conjecturing that four groups will correspond to all 12 different conditions)
cl <- kmeans(cluster.data, centers = 12)

#copy cluster result into dataframe
plot_data <- na.omit(data_avg[,-c(22)])
plot_data$Cluster <- as.factor(cl$cluster)

plot_data$Obstacle <- as.factor(plot_data$Obstacle)
plot_data$Task <- as.factor(plot_data$Task)

```

```{r}
# Perform PCA
pca_result <- prcomp(cluster.data, rank. = 2)  # reduce to 2 dimensions for visualization

loadings <- pca_result$rotation

# Add PCA results to the original data frame
plot_data$PC1 <- pca_result$x[, 1]
plot_data$PC2 <- pca_result$x[, 2]

# Use ggplot2 to create the PCA scatter plot colored by clusters
ggplot(plot_data, aes(x = PC1, y = PC2, color = as.factor(Cluster))) +
  geom_point() +
  scale_color_manual(values = c("purple", 'steelblue', 'green', 'orange','pink','grey','black','darkblue','darkgreen','yellow','blue','red')) + # Customize colors if needed
  theme_minimal() +
  labs(title = "PCA of k-Means Clusters (12 Centers)", color = "Cluster")

```

## Gaussian Mixture (GMM)
```{r}
#copy data into a new dataframe with 17 independent variables
cluster.data <- data_avg[,-c(1,2,18,19,22)]
cluster.data$Gender <- ifelse(data_avg$Gender == "female", 1, 0)
cluster.data[,1:14] <- scale(cluster.data[,c(1:14,16:17)])
cluster.data <- na.omit(cluster.data)

gmm.result <- Mclust(cluster.data)
summary(gmm.result)

```

```{r}
pca_result <- prcomp(cluster.data, rank. = 2)

plot_data <- na.omit(data_avg[,-c(22)])
plot_data$Cluster <- as.factor(gmm.result$classification)

plot_data$Obstacle <- as.factor(plot_data$Obstacle)
plot_data$Task <- as.factor(plot_data$Task)

plot_data$PC1 <- pca_result$x[, 1]
plot_data$PC2 <- pca_result$x[, 2]

ggplot(plot_data, aes(x = PC1, y = PC2, color = factor(Cluster), shape = factor(Condition))) +
    geom_point() +
    theme_minimal() +
    labs(color = "Cluster", shape = "Condition")

```


## Random Forest
```{r}
cluster.data <- data_avg[,-c(1,18,19,22)]
cluster.data$Gender <- ifelse(data_avg$Gender == "female", 1, 0)
cluster.data[,c(2:15,17:18)] <- scale(cluster.data[,c(2:15,17:18)])
cluster.data <- na.omit(cluster.data)
names(cluster.data) <- make.names(names(cluster.data))
rf_model <- randomForest(Condition ~ ., data = cluster.data)
print(rf_model)
predictions <- predict(rf_model, newdata=cluster.data)
predictions

```
```{r}
# Predicting on the same dataset used for training just as an example
predictions <- predict(rf_model, cluster.data)

predictions_rounded <- round(predictions)

# Assuming that Condition is a numeric column that represents integer classes
actual_values <- cluster.data$Condition
accuracy <- sum(predictions_rounded == actual_values) / length(actual_values)

# Calculate RMSE
rmse <- sqrt(mean((predictions - actual_values)^2))

accuracy
```

## GBM
```{r}
cluster.data <- data_avg[,-c(1,18,19,22)]
cluster.data$Gender <- ifelse(data_avg$Gender == "female", 1, 0)
cluster.data[,c(2:15,17:18)] <- scale(cluster.data[,c(2:15,17:18)])
cluster.data <- na.omit(cluster.data)
names(cluster.data) <- make.names(names(cluster.data))

gbm_model <- gbm(Condition ~ ., data=cluster.data, distribution="gaussian", n.trees=100, interaction.depth=3)

summary(gbm_model)

gbm_predictions <- predict(gbm_model, newdata=cluster.data, n.trees=100)


# Predicting on the same dataset used for training as an example
predicted_classes <- predict(gbm_model, newdata = cluster.data, n.trees = gbm_model$n.trees, type = "response")


predictions_rounded <- round(predicted_classes)

actual_classes <- cluster.data$Condition  # Make sure this is the correct column for actual class labels
accuracy <- mean(predictions_rounded == actual_classes)

# Predict using the GBM model
predictions <- predict(gbm_model, newdata = cluster.data, n.trees = gbm_model$n.trees)

# Round predictions to nearest integer
predictions_rounded <- round(predictions)

# Assuming that Condition is a numeric column that represents integer classes
actual_values <- cluster.data$Condition

# Calculate accuracy
accuracy <- sum(predictions_rounded == actual_values) / length(actual_values)

accuracy
```

## XGBoost

```{r}
# Ensure that 'Condition' is a factor and get its levels as numeric values
num_classes = length(unique(cluster.data$Condition))
cluster.data$Condition <- as.numeric(as.factor(cluster.data$Condition)) - 1

# Check the range of 'Condition' to make sure it's within [0, num_class)
if(min(cluster.data$Condition) < 0 || max(cluster.data$Condition) >= num_classes) {
  stop("Labels are not within the correct range.")
}

# Update the DMatrix
data_matrix <- xgb.DMatrix(data = as.matrix(cluster.data[, -which(names(cluster.data) == "Condition")]),
                           label = cluster.data$Condition)

# Update the parameters (make sure num_class is set correctly)
params <- list(
  objective = "multi:softprob",
  eval_metric = "mlogloss",
  max_depth = 6,
  eta = 0.3,
  num_class = num_classes,  # This should be the number of unique classes
  nthread = 2
)

# Train the model
xgb_model <- xgb.train(params = params,
                       data = data_matrix,
                       nrounds = 100,
                       watchlist = list(train = data_matrix),
                       verbose = 0)

# Make predictions
pred_probs <- predict(xgb_model, data_matrix)
num_data <- nrow(cluster.data)

# Reshape the prediction probabilities and find the class with the maximum probability
pred_classes <- matrix(pred_probs, nrow = num_data, byrow = TRUE)
predicted_labels <- max.col(pred_classes) - 1  # Subtract 1 because max.col is 1-indexed

# Actual labels (make sure these are zero-indexed as well)
actual_labels <- cluster.data$Condition

# Compute accuracy
accuracy <- mean(predicted_labels == actual_labels)
 
accuracy
```
This is the accuracy with full dataset's condition compared with predicted condition

```{r}
# Example of simple train-test split
set.seed(123)  # for reproducibility
train_indices <- sample(1:nrow(cluster.data), 0.8 * nrow(cluster.data))
test_indices <- setdiff(1:nrow(cluster.data), train_indices)

train_data <- cluster.data[train_indices, ]
test_data <- cluster.data[test_indices, ]

train_matrix <- xgb.DMatrix(data = as.matrix(train_data[, -which(names(train_data) == "Condition")]),
                            label = train_data$Condition)
test_matrix <- xgb.DMatrix(data = as.matrix(test_data[, -which(names(test_data) == "Condition")]),
                           label = test_data$Condition)

# Train and evaluate the model using the train and test datasets
# Make predictions on the test set
test_predictions_probs <- predict(xgb_model, test_matrix)
num_test_data <- nrow(test_data)

# Convert probabilities to class predictions
test_pred_classes <- matrix(test_predictions_probs, nrow = num_test_data, byrow = TRUE)
test_predicted_labels <- max.col(test_pred_classes) - 1

# Actual test labels
test_actual_labels <- test_data$Condition

# Calculate accuracy
test_accuracy <- mean(test_predicted_labels == test_actual_labels)

# Print the accuracy
test_accuracy

```
This is the test accuracy that I split dataset into train and test. After using the training dataset to build the model, I used the testing dataset to test the model, and the accuracy is still 1.

```{r}
importance_matrix <- xgb.importance(feature_names = colnames(cluster.data[, -which(names(cluster.data) == "Condition")]), model = xgb_model)
print(importance_matrix)
```
CV Step Time, CV Stride Time are the features contributed the most to XGBoost's performance. 

<!---

## Visualization
```{r, include = FALSE}
#Step Length
boxplot(data_avg$`%CV Step Length (cm.)`~data_avg$Condition, 
        xlab = "Condition", ylab = "%CV Step Length (cm.)")
boxplot(data_avg$`Mean Step Length (cm.)`~data_avg$Condition, 
        xlab = "Condition", ylab = "Mean Step Length (cm.)")

#Velocity
boxplot(data_avg$`Velocity (cm./sec.)`~data_avg$Condition, 
        xlab = "Condition", ylab = "Velocity")

#Cadence
boxplot(data_avg$`Cadence (steps/min.)`~data_avg$Condition, 
        xlab = "Condition", ylab = "Cadence (steps/min.)")

#Step Time
boxplot(data_avg$`Step Time (sec.)`~data_avg$Condition, 
        xlab = "Condition", ylab = "Mean Step Time (sec.)")
boxplot(data_avg$`%CV Step Time (sec.)`~data_avg$Condition, 
        xlab = "Condition", ylab = "%CV Step Time (sec.)")

#Total D. Support
boxplot(data_avg$`%CV Total D. Support (sec.)`~data_avg$Condition, 
        xlab = "Condition", ylab = "%CV Total D. Support (sec.)")
boxplot(data_avg$`Total D. Support (sec.)`~data_avg$Condition, 
        xlab = "Condition", ylab = "Mean Total D. Support (sec.)")


#Stride Length
boxplot(data_avg$`%CV Stride Length (cm.)`~data_avg$Condition, 
        xlab = "Condition", ylab = "%CV Stride Length (cm.)")
boxplot(data_avg$`Mean Stride Length (cm.)`~data_avg$Condition, 
        xlab = "Condition", ylab = "Mean Stride Length (cm.)")

#Stride Width
boxplot(data_avg$`%CV Stride Width (cm.)`~data_avg$Condition, 
        xlab = "Condition", ylab = "%CV Stride Width (cm.)")
boxplot(data_avg$`Stride Width (cm.)`~data_avg$Condition, 
        xlab = "Condition", ylab = "Mean Stride Width (cm.)")

#Stride Time
boxplot(data_avg$`Stride Time (sec.)`~data_avg$Condition, 
        xlab = "Condition", ylab = "Mean Stride Time (sec.)")
boxplot(data_avg$`%CV Stride Time (sec.)`~data_avg$Condition, 
        xlab = "Condition", ylab = "%CV Stride Time (sec.)")

```


## Condition 1, 5, 6
```{r, include = FALSE}
data_156 <- data_avg[data_avg$Condition %in% c('1', '5', '6'),]

create_boxplot <- function(data, variable, title) {
  ggplot(data, aes(x = as.factor(Condition), y = .data[[variable]])) +
    geom_boxplot() +
    stat_summary(fun = mean, geom = "line", aes(group = 1), 
                 linetype = "dashed", color = "red", linewidth = 0.5) +
    labs(title = title, x = "Condition", y = title) +
    theme_minimal()
}

# List of variable names as they appear in your dataframe
variables <- list(
  `%CV Step Length (cm.)` = "%CV Step Length (cm.)",
  `Mean Step Length (cm.)` = "Mean Step Length (cm.)",
  `Velocity (cm./sec.)` = "Velocity (cm./sec.)",
  `Cadence (steps/min.)` = "Cadence (steps/min.)",
  `Step Time (sec.)` = "Step Time (sec.)",
  `%CV Step Time (sec.)` = "%CV Step Time (sec.)",
  `%CV Total D. Support (sec.)` = "%CV Total D. Support (sec.)",
  `Total D. Support (sec.)` = "Total D. Support (sec.)",
  `%CV Stride Length (cm.)` = "%CV Stride Length (cm.)",
  `Mean Stride Length (cm.)` = "Mean Stride Length (cm.)",
  `%CV Stride Width (cm.)` = "%CV Stride Width (cm.)",
  `Stride Width (cm.)` = "Stride Width (cm.)",
  `Stride Time (sec.)` = "Stride Time (sec.)",
  `%CV Stride Time (sec.)` = "%CV Stride Time (sec.)"
)

# Create and save plots for each variable
for (var_name in names(variables)) {
  var_label <- variables[[var_name]]
  plot <- create_boxplot(data_156, var_name, var_label)
  print(plot)
}
```

## Condition 2, 7, 8
```{r, include = FALSE}
data_278 <- data_avg[data_avg$Condition %in% c('2', '7', '8'),]

for (var_name in names(variables)) {
  var_label <- variables[[var_name]]
  plot <- create_boxplot(data_278, var_name, var_label)
  print(plot)
}

```


## Condition 3, 9, 10
```{r, include = FALSE}
data_3910 <- data_avg[data_avg$Condition %in% c('3', '9', '10'),]

for (var_name in names(variables)) {
  var_label <- variables[[var_name]]
  plot <- create_boxplot(data_3910, var_name, var_label)
  print(plot)
}
```

## Condition 4, 11, 12
```{r, include = FALSE}
data_41112 <- data_avg[data_avg$Condition %in% c('4', '11', '12'),]

for (var_name in names(variables)) {
  var_label <- variables[[var_name]]
  plot <- create_boxplot(data_41112, var_name, var_label)
  print(plot)
}
```

## Condition 1, 2, 3, 4
```{r, include = FALSE}
data_1234 <- data_avg[data_avg$Condition %in% c('1', '2', '3','4'),]

for (var_name in names(variables)) {
  var_label <- variables[[var_name]]
  plot <- create_boxplot(data_1234, var_name, var_label)
  print(plot)
}

```

## Condition 5, 7, 9, 11
```{r, include = FALSE}
data_57911 <- data_avg[data_avg$Condition %in% c('5', '7', '9','11'),]

for (var_name in names(variables)) {
  var_label <- variables[[var_name]]
  plot <- create_boxplot(data_57911, var_name, var_label)
  print(plot)
}

```


## Condition 6, 8, 10, 12
```{r, include = FALSE}
data_681012 <- data_avg[data_avg$Condition %in% c('6', '8', '10','12'),]

for (var_name in names(variables)) {
  var_label <- variables[[var_name]]
  plot <- create_boxplot(data_681012, var_name, var_label)
  print(plot)
}

```


## Regression
```{r, include = FALSE}
subset = data_avg[,-1]
full.model <- lm(subset$Condition ~., data = subset)
summary(full.model)
```
### BIC Variable Selection
```{r, include = FALSE}
#step(full.model, direction = "both", k = log(length(subset)))
```
Result shown that Cadence and CV Stride Time contribute more to predict Condition, so that we might can infer Condition might cause greater influence two these two factors.
```{r, include = FALSE}
aic.both.model <- lm(formula = subset$Condition ~ `%CV Stride Time (sec.)` + 
                       `Cadence (steps/min.)`, data = subset)
summary(aic.both.model)
```


```{r, include = FALSE}
#Split into two parts to see scatter plots

scatterplotMatrix(~ data_avg$Condition + data_avg$`Mean Step Length (cm.)` + data_avg$`Mean Stride Length (cm.)` + data_avg$`Stride Width (cm.)` + data_avg$`Step Time (sec.)` + data_avg$`Stride Time (sec.)` + data_avg$`Total D. Support (sec.)` + data_avg$`Velocity (cm./sec.)`)

scatterplotMatrix(~ data_avg$Condition + data_avg$`Cadence (steps/min.)` + data_avg$`%CV Step Length (cm.)` + data_avg$`%CV Stride Length (cm.)` + data_avg$`%CV Stride Width (cm.)` + data_avg$`%CV Step Time (sec.)` + data_avg$`%CV Stride Time (sec.)` + data_avg$`%CV Total D. Support (sec.)`)
```

CV Step Time, CV Stride Time, Velocity, Mean Step Time, Cadence have comparatively stronger relationship with Condition

-->







